---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ToyotaSiennaGasMileage

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/jarad/ToyotaSiennaGasMileage.svg?branch=master)](https://travis-ci.org/jarad/ToyotaSiennaGasMileage)
<!-- badges: end -->

ToyotaSiennaGasMileage provides gas consumption data on a 2011 Toyota Sienna
XLE from purchase through today. The data are available for those who are 
studying gas consumption, but also available for anybody interested in plotting
or modeling a time series with irregular observations. 

Data were originally recorded by hand. These sheets were scanned and digitized 
into csv files that match the scanned sheets. An R script is used to combine
all the files into a single R data.frame included in the package as 
`ToyotaSiennaGasMileage`. Thus, these files provide an example data management
process for manually recorded data.


## Installation

You can install the released version of ToyotaSiennaGasMileage from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("ToyotaSiennaGasMileage")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jarad/ToyotaSiennaGasMileage")
```

## Example

Here is a graphical display of the data.

```{r example}
library(ToyotaSiennaGasMileage)
library(ggplot2)

ggplot(ToyotaSiennaGasMileage, 
       aes(x = date, y = miles/gallons)) +
  geom_point()
```


